A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-21 main.tex
Grammarly

In this section, we define full reduction for \LMD.
Before giving the definition of reduction, we define two substitutions.
Substituition $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its definition here.
Substituition $M[\alpha \mapsto \epsilon]$ is defined below.

@@

$\longrightarrow_\beta$ is normal $\beta-$reduction in lambda calculus.
$\longrightarrow_\blacklozenge$ means that when a quoted code is unquoted, it become the original code.
$\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
where $\epsilon$ is substituted to the stage variable.
Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD.
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
$\%_\alpha$, the symbol for CSP, is disappeared when $\epsilon$ is substituted to $\alpha$.
$\TB_\alpha$ and $\TBL_\alpha$ is disappeared in the same way as $\%_\alpha$.

@@

In this section, we define the type system of \LMD.
Especially, we discuss on the type equality of \LMD in detail
because it is the main contribution of this paper.
\LMD is developed on the basis of \LTP but there is no type equivalence rules in \LTP.

@@

% 通常のルール
We show typing rules of \LMD in Figure \ref{fig:typing-rules}.
The rules \TVar , \TAbs, and \TApp\ are almost same as those in simply typed lambda calculus 
if you ignore stage annotations and kind checking.
The rule \TVar\ means that a variable can appear only at the stage in which it is declared.
It checks the type of variable $x$, $\tau$, has the proper kind for terms, $*$.
\TAbs\ also checks the kind of the type.

@@

% 2つの設計手法と今回採用した理由
When we design type equivalence rules of \LMD, there are two design choices.
One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
Another is defining type equivalence directly by combination of type equivalence rules.
We adopt the latter one because it is convenient to handle CSP in the type equivalence.

>>>>

In this section, we define full reduction for \LMD.
Before giving the definition of reduction, we define two substitutions.
Substitution $M[x\mapsto N]$ is the normal capture-avoiding substitution, and we omit its definition here.
Substitution $M[\alpha \mapsto \epsilon]$ is defined below.

@@

$\longrightarrow_\beta$ is normal $\beta-$reduction in lambda calculus.
$\longrightarrow_\blacklozenge$ means that when a quoted code is unquoted, it becomes the original code.
$\longrightarrow_\Lambda$ means that a stage abstraction applied to the empty stage $\epsilon$ reduces to the body of abstraction
where $\epsilon$ is substituted to the stage variable.
Application of a non-$\epsilon$ stage to a stage abstraction is prohibited in order to simplify \LMD.
There is no reduction rule for CSP as with Hanada and Igarashi \cite{Hanada2014}.
$\%_\alpha$, the symbol for CSP, is disappeared when $\epsilon$ is substituted to $\alpha$.
$\TB_\alpha$ and $\TBL_\alpha$ is disappeared in the same way as $\%_\alpha$.

@@

In this section, we define the type system of \LMD.
Especially, we discuss on the type equality of \LMD in detail
because it is the main contribution of this paper.
\LMD is developed on the basis of \LTP but there are no type equivalence rules in \LTP.

@@

% 通常のルール
We show typing rules of \LMD in Figure \ref{fig:typing-rules}.
The rules \TVar , \TAbs, and \TApp\ are almost the same as those in simply typed lambda calculus 
if you ignore stage annotations and kind checking.
The rule \TVar\ means that a variable can appear only at the stage in which it is declared.
It checks the type of variable $x$, $\tau$, has the proper kind for terms, $*$.
\TAbs\ also checks the kind of the type.

@@

% 2つの設計手法と今回採用した理由
When we design type equivalence rules of \LMD, there are two design choices.
One is defining type equivalence by $\beta$-equality after we define $\beta$-reduction of types.
Another is defining type equivalence directly by a combination of type equivalence rules.
We adopt the latter one because it is convenient to handle CSP in the type equivalence.
